%------------------------
% Resume in Latex
% Author : Sam Zhang
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\onehalfspacing

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    #1 & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Sam Zhang} \\ \vspace{1pt}
  \small +1 (438) 630-2638 $|$ \href{mailto:sam.zijing.zhang@gmail.com}{\underline{sam.zijing.zhang@gmail.com}}  \\
  \href{https://linkedin.com/in/zhang-sam}{\underline{linkedin.com/in/zhang-sam}} $|$
  \href{https://github.com/SamZhang02}{\underline{github.com/SamZhang02}} $|$
  \href{https://cs.mcgill.ca/~szhang139}{\underline{cs.mcgill.ca/$\sim$szhang139}}\\
\end{center}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{McGill University}}{Montreal, QC}
{B.A., Joint Computer Science and Statistics}{Aug. 2022 -- May. 2025 (Expected)}
\resumeItem{\textbf{GPA:} 3.94/4}
\resumeItem{\textbf{Relevant Courseworks:}}
\resumeItemListStart
\resumeItem{Natural Language Processing}
\resumeItem{Computational Linguistics}
\resumeItem{Data Structures and Algorithms}
\resumeItem{Programming Languages and Paradigms}
\resumeItem{Probabilities}
\resumeItem{Statistics}
\resumeItemListEnd
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{{\textbf{Software Developer Intern}} $|$ \emph{React, C\#, ASP.NET, SQL}}{Sept. 2023 - Present}
{Ceridian HCM}{Toronto, Canada (Remote)}
\resumeItemListStart
\resumeItem{
  Full-stack web development for Dayforce, a cloud-based human capital management (HCM) platform.
}
\resumeItem{
  Developing the micro-frontend of the Dayforce application's position management feature using  \textbf{TypeScript React} and backend microservices  using \textbf{C\#} and \textbf{ASP.NET}.}
\resumeItemListEnd
\resumeSubheading
{{\textbf{Machine Learning R\&D Intern}} $|$ \emph{TensorFlow, Python, Scala, SQL}}{May. 2023 - Aug. 2023}
{Meituan}{Shanghai, China (On-Site)}
\resumeItemListStart
\resumeItem{Recommender system research and development for Meituan, the largest local life service platform in China.}
\resumeItem{Worked on the tuning of the Click-Through Rate (CTR) model, a binary classification feedforward artificial neural network. Aiming to refine its understanding of the ad and the ad-user context, thereby improving its performance in CTR predictions.}
\resumeItem{Conducted 2 offline experiments from start to finish with following the internal pipeline; cleaning, pre-processing, and extracting the features from over 100TB of data per experiment using the \textbf{Hadoop ecosystem (Hive, Spark, Mapreduce, \dots)}, and training using \textbf{TensorFlow}. The two experiments being:}
{
  \resumeItemListStart
  \resumeItem{Integrated a new set of image embeddings into the CTR model to assess potential performance increases.}
  \resumeItem{Computed similarity measures between the user's historical search queries' keywords and ad canidates' keywords, and integrated them as features into the CTR model.}
  \resumeItemListEnd
}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://mcgill.courses}{\textbf{mcgill.courses}} $|$ \emph{TypeScript, React, TailwindCSS, Rust, MongoDB}}{April. 2023 - Present}
\resumeItemListStart
\resumeItem{Developing and maintaining  an open-source, ad-free search and review platform for courses offered and instructors teaching at McGill University.}
\resumeItem{Responsible for the front-end development of the website using \textbf{TypeScript}, \textbf{React}, and \textbf{TailwindCSS}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Programming Languages}{: Python, R, SQL, Scala, C++ TypeScript, JavaScript, Java, C\#} \\
        \textbf{Databases}{: SQLite, HiveSQL, MySQL, MongoDB}\\
        \textbf{Frameworks \& Libraries}{: TensorFlow}\\
        \textbf{Tools}{: Git, \LaTeX, Spark, Hadoop}\\
        \textbf{Languages Spoken}{: English, French, Chinese Mandarin, Chinese Cantonese}\\
        }}
\end{itemize}
%-------------------------------------------


\end{document}
