%------------------------s
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\onehalfspacing

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    #1 & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Sam Zhang} \\ \vspace{1pt}
  \small (438) 630-2638 $|$ \href{mailto:sam.zijing.zhang@gmail.com}{\underline{sam.zijing.zhang@gmail.com}}  \\
  \href{https://linkedin.com/in/zhang-sam}{\underline{linkedin.com/in/zhang-sam}} $|$
  \href{https://github.com/SamZhang02}{\underline{github.com/SamZhang02}} $|$
  \href{https://cs.mcgill.ca/~szhang139}{\underline{cs.mcgill.ca/$\sim$szhang139}}
\end{center}
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{{\textbf{Machine Learning Intern}} $|$ \emph{TensorFlow, Python, Scala, Java, SQL}}{May. 2023 - Present}
{Meituan}{Shanghai, China}
\resumeItemListStart
\resumeItem{Contributed to Meituan, the largest local life service platform in China's advertisement recommendation system.}
\resumeItem{Participated in the research and development of the click-through rate (CTR) model for the Dianping app's homepage ad.}
\resumeItem{Conducted various offline experiments to evaluate model performance and iteratively improved the models.}
\resumeItem{Performed big data analysis and feature engineering using the \textbf{Hadoop ecosystem (Hive, Spark, \ldots)}}
\resumeItem{Modeled, trained, and fine-tuned the models using \textbf{TensorFlow}.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://mcgill.courses}{\textbf{mcgill.courses}} $|$ \emph{TypeScript, React, TailwindCSS, Rust, MongoDB}}{April. 2023 - Present}
\resumeItemListStart
\resumeItem{Developed an open-source, ad-free search and review platform for courses offered and instructors teaching at McGill University.}
\resumeItem{Responsible for the front-end development of the website using \textbf{TypeScript}, \textbf{React}, and \textbf{TailwindCSS}.}
\resumeItem{Collaborated with the back-end, interacting with the \textbf{Rust} and \textbf{MongoDB} components through REST APIs.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/SamZhang02/obsidian-latex-algorithms}{\textbf{LaTeX Algorithms}} $|$ \emph{TypeScript}}{Feb. 2023}
\resumeItemListStart
\resumeItem{Developed a \textbf{TypeScript} plugin for the Obsidian markdown editor that parses user input and automatically replaces it with the corresponding LaTeX shortcut, streamlining the writing of algorithm blocks and mathematical proofs.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/SamZhang02/STONK}{\textbf{STONK}} $|$ \emph{Python, SQLite}}{Dec. 2022}
\resumeItemListStart
\resumeItem{Created a Discord chat bot using the Discord.py library and the yfinance open-source library, enabling users to query live and historical stock market information.}
\resumeItem{Implemented a robust stock information retrieval mechanism and a subscription system for users to receive automatic notifications on market trends.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{McGill University}}{Montreal, QC}
{B.A., Joint Computer Science and Statistics}{ Sept. 2022 -- May 2025 (Expected)}
\resumeItem{GPA: 3.94/4}
\resumeSubheading
{\textbf{Champlain College}}{St-Lambert, QC}
{DEC, Social Science: Commerce}{Aug. 2020 -- May. 2022}
\resumeItem{Social Science Certificate of Merit: Highest Achievement in Economics}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Languages}{: Python, TypeScript, Java, JavaScript, OCaml, C++, Scala, SQL} \\
                \textbf{Databases}{: SQLite, PostgreSQL, MongoDB}\\
                \textbf{Frameworks \& Libraries}{: React, TailwindCSS, TensorFlow}\\
                \textbf{Tools}{: Git, HTML/CSS, \LaTeX, Spark, HDFS}\\
                \textbf{Languages Spoken}{: English, French, Mandarin, Cantonese}\\
          }}
\end{itemize}
%-------------------------------------------

\end{document}