%------------------------
% Resume in Latex
% Author : Sam Zhang
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.1pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    #1 & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Sam Zhang} \\ \vspace{1pt}
  \small +1 (438) 630-2638 $|$ \href{mailto:sam.zijing.zhang@gmail.com}{\underline{sam.zijing.zhang@gmail.com}}  \\
  \href{https://linkedin.com/in/zhang-sam}{\underline{linkedin.com/in/zhang-sam}} $|$
  \href{https://github.com/SamZhang02}{\underline{github.com/SamZhang02}} $|$
  \href{https://cs.mcgill.ca/~szhang139}{\underline{cs.mcgill.ca/$\sim$szhang139}}\\
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{McGill University}}{Montreal, Canada}
{B.A., Joint Computer Science and Statistics}{Aug. 2022 -- May 2025 (Expected)}
\resumeItem{GPA: 3.95/4}
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{{\textbf{Software Developer Intern}} $|$ \emph{TypeScript, React, C\#, .NET, SQL}}{Sept. 2023 - Present}
{Dayforce}{Toronto, Canada}
\resumeItemListStart
\resumeItem{
  Contributed to full-stack web development on Dayforce, a leading cloud-based human capital management platform. Developed the frontend for Dayforce's position management feature with \textbf{TypeScript} and \textbf{React}, and the backend microservices in \textbf{C\#} and \textbf{.NET}.}
  \resumeItem{Worked as a core member in the revamp of the frontend UI, enhancing user experience and client accessibility. 
    Implemented accurate validation logic, and optimizing browser-side performance while ensuring active collaboration with Product and UI/UX teams.}
  \resumeItem{
  Cleared tech debts for the team, designed and implemented automated tests using tools like Cypress and Specflow, thereby increasing application reliability and code robustness.
}
\resumeItemListEnd
\resumeSubheading
{{\textbf{Machine Learning Research Intern}} $|$ \emph{Hadoop, TensorFlow, Python, Scala, SQL}}{May 2023 - Aug. 2023}
{Meituan}{Shanghai, China}
\resumeItemListStart
\resumeItem{
Engaged in research and development for Meituan, the largest leading local service platform in China, focusing on the advertisement recommender system.
}
\resumeItem{
Worked on the Click-Through-Rate (CTR) model by deepening its comprehension of both ad context and user interactions, aiming to improve prediction accuracy.}
\resumeItem{
  Conducted two comprehensive offline model experiments, 
  handling tasks from initiation to conclusion. 
  Managed the distributed cleaning, pre-processing, 
  and feature extraction from datasets of over 150TB per experiment utilizing tools 
  like \textbf{Hive, Spark, MapReduce} within the Hadoop ecosystem, improving the model's understanding of the ad-user context. 
  Subsequently, developed deployable models using \textbf{TensorFlow} for further online testing.
}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://mcgill.courses}{\textbf{mcgill.courses}} $|$ \emph{TypeScript, React, Rust, MongoDB}} {Apr. 2023 - Present}
\resumeItemListStart
\resumeItem{Working on an open-source, ad-free platform for easy search and review of courses and instructors at McGill University, allowing students to have a unified platform for course information and feedbacks.}
\resumeItem{Developed the application front-end using \textbf{TypeScript}, \textbf{React}, and \textbf{TailwindCSS}, ensuring a smooth browser-side user experience.}
\resumeItem{Implemented and deployed RESTful APIs using \textbf{Rust} for server-side logic and \textbf{MongoDB} for database management, with data retrieval efficiency and system scalability in mind.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/SamZhang02/llmbda}{\textbf{Llmbda}} $|$ \emph{Pytorch, Python}} {Dec. 2023}
\resumeItemListStart
\resumeItem{Prompted and fine-tuned Meta's open-sourced LLM \textbf{Llama2} to generate a formal syntax tree output to investigate Large Language Models' (LLM) ability to understand logical semantics in semi-formal natural language.}
\resumeItem{Developed from scratch unique evaluation metrics to evaluate model performances based on their syntax tree output, and pipelined the evaluation process using Python.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/SamZhang02/obsidian-latex-algorithms.git}{\textbf{Obsidian LateX Algorithm}} $|$ \emph{TypeScript}} {Mar. 2023}
\resumeItemListStart
\resumeItem{Developed with \textbf{TypeScript} a plugin for the electron-based markdown editor app \textit{Obsidian} to facilitate the process of writing mathematical algorithms and pseudocodes within the editor.}
\resumeItem{Acquired over 3,000+ downloads.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Python, TypeScript, JavaScript, Java, Scala, C, C++, C\#, Rust, SQL} \\
        \textbf{Databases}{: SQLite, HiveQL, MySQL, MongoDB}\\
        \textbf{Frameworks \& Libraries}{: React, TailwindCSS, TensorFlow, PyTorch, .NET}\\
        \textbf{Tools}{: Git, Docker, Spark, Hadoop}\\
        \textbf{Languages Spoken}{: English, French, Chinese Mandarin, Chinese Cantonese}\\
        }}
\end{itemize}
%-------------------------------------------

\end{document}

